Development of User-friendly\\System Identification Techniques

### 2015-11-01 ch02-qlogms/logMS_IMTC.tex
Import SYSID2012 paper

\TODO{reshape figures}
\TODO{rename labels}
\TODO{import specific bib items}
% \begin{abstract}
% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
% Periodic signals are very popular in many advanced dynamic signal analyzers.
% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
% \end{abstract}

@@

  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
  To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
  In continuous time such a system can be described by a transfer function of the form
  \begin{equation}
    G\left(s \right) = \frac{\dc}
                            {             \frac{s^2}
                                               {\wn^2} 
                             + 2 \damping \frac{s}
                                               {\wn}
                             + 1
                            }
  \text{.}
  \label{eq:secondOrderSystemCT}
  \end{equation}
  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
  The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
  The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.

@@

\subsection{Multisine Excitations}
  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ commensurate frequency components:
  \begin{equation}
    u \left( t\right) = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(2\pi f_k t + \phi_k \right)
  \text{.}
  \label{eq:MultisineCT}
  \end{equation}
  In this expression, $f_k$ represents the $k^{\text{th}}$ excited frequency component.
  $A_k$ is the amplitude and $\phi_k$ the phase of the $k^{\text{th}}$ spectral line.
  We limit ourselves, without loss of generality, to random phase multisines.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
    the amplitude of the spectral lines $A_k$ and
    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.

@@

  Each decade within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains the same number of frequency components such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.

  To return to the FRF, in Section \ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
  As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
  bandwidth, one expects an equal variance for each system, as will be shown in Section \ref{sec:bestFrequencyResolution}.

@@

  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $[0,1]$.
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

>>>>

\TODO{reshape figures}
\TODO{rename labels}
% \begin{abstract}
% The logarithmic distribution of spectral lines in excitation signals is widely used to measure the transfer functions of dynamic systems over a wide frequency band, covering several decades.
% Periodic signals are very popular in many advanced dynamic signal analyzers.
% Generating multitone periodic signals requires an equidistant frequency grid which conflicts with the logarithmic distribution, especially at the low frequencies.
% In this paper we offer an elegant solution to get around this problem using an improved choice for the amplitude spectrum of the multitone.
% We also offer a simple way to tune the frequency spacing of such a signal to allow for robust identification of the system under test.
% \end{abstract}

@@

  Such a system can be decomposed into a series of first and second order systems by the partial fraction expansion.
  To study the behavior of one sub-system, we inspect a generic second order system $G\left( s \right)$.
  In continuous time such a system can be described by a transfer function of the form
  \begin{equation}
    G\left(s \right) = \frac{\dc}
                            {             \frac{s^2}
                                               {\wn^2} 
                             + 2 \damping \frac{s}
                                               {\wn}
                             + 1
                            }
  \text{.}
  \label{eq:secondOrderSystemCT}
  \end{equation}
\TODO{This is actually wrong, rather, it should be $\frac{as-b}{cs^2 + ds + 1}$. However, the difference in information is rather small around the actual resonance. See script in NnF folder.}
\TODO{write out in partial fraction expansion, use script to show that in practice, only a few parameters matter. This will be well-approximated by considering only the second order system of the paper.}

  The DC gain $\dc$, the (relative) damping $\damping$ and the natural pulsation $\wn$ are a more intuitive parametrization for this system than the generic polynomial coefficients $a_i$ and $b_i$ used in \eqref{eq:model}.
  The corresponding resonance pulsation is $\wR \isdef \wn \sqrt{1-\damping^2}$.
  The $3\unit{dB}$ bandwidth around the resonance is given by $\wdB = 2\damping\wn$ for systems that have a sufficiently low damping.

@@

\subsection{Multisine Excitations}
  To excite the system under test we will use multisine excitations \citep{Pintelon2001} with $F$ frequency components:
  \begin{equation}
    u \left( t\right) = \frac{1}{\sqrt{F}}
   \sum_{k=1}^{F} 
     A_k 
     \sin 
       \left(2\pi f_k t + \phi_k \right)
  \text{.}
  \label{eq:MultisineCT}
  \end{equation}
  In this expression, $f_k$ represents the $k^{\text{th}}$ excited frequency component.
  $A_k$ is the amplitude and $\phi_k$ the phase of the $k^{\text{th}}$ spectral line.
  We limit ourselves, without loss of generality, to random phase multisines.
  Hence, $\phi_k$ is the outcome of a uniform random process over $\left[0,2\pi\right[$.
  This leaves two sets of free parameters to create a signal that suits our needs:
    the amplitude of the spectral lines $A_k$ and
    the frequency grid $\left\{f_1, \ldots, f_F \right\}$.
  For simplicity, we will assume this grid is sorted, i.e. $f_1 < f_2 < \ldots < f_F$.
  Note that the $k^{\text{th}}$ term in \eqref{eq:MultisineCT} is has a period $T_k \isdef f_k^{-1}$.

  Consequently, the complete multisine has a period of
  \begin{equation}
    T_{u(t)}  = \lcm \set{T_1, \ldots, T_F}
      = \lcm \set{f_1^{-1}, \ldots, f_F^{-1}}
    \text{,}
  \end{equation}
  where the least common (integer) multiple of the real values $T_k$ is defined as
  \begin{equation}
    \lcm \set{T_1, \ldots, T_F} \isdef
      \min \set{T \given{\forall i \in \set{1,\ldots,F}, \exists n_i \in \NaturalNumbers: n_i T_i = T }}
      \text{.}
   \end{equation}
  Note that this minimum doesn't always exist (e.g. when $f_1 = 1 \unit{Hz}$ and $f_F = \pi \unit{Hz}$), in such cases the multisine is aperiodic.

@@

  Each decade that is completely  within the resulting set of excited frequencies $\set{f_1, \ldots, f_F}$ contains
   \begin{equation}
     \floor{\frac{\log (10 f) - \log( f )}{\log \alpha}}
         = \floor{\log_{\alpha} 10}
   \end{equation}
   excited frequency lines. 
   I.e. the same number of frequency components is present per decade, such that the power in each decade is identical when a constant amplitude spectrum ($A_k = A_{\mathrm{in}}$) is used.
   Obviously, the same argument can be held for any relative bandwidth (e.g. octave or even the $\wdB$ of a particular system).

  To return to the FRF, in Section~\ref{sec:optimAlpha} we will show that for a dense logarithmic frequency grid, any second order system with damping $\damping$ and a resonance within the bulk of the frequency grid, will receive the same number of frequency lines in its $3 \unit{dB}$ bandwidth regardless of the actual value of the resonance frequency.
  As most of the information of such systems is obtained from the measurements at frequencies inside the $3 \unit{dB}$
  bandwidth, one expects an equal variance for each system, as will be shown in Section~\ref{sec:bestFrequencyResolution}.

@@

  Instead of using \eqref{eq:theoreticalBestVariationOmega} to establish the influence of the resonance frequency, we apply an equivalent approach that is more intuitive to interpret.
  \TODO{show $\alpha$ and $\beta$ graphically (cfr. poster)}
  We choose the resonance frequency of the systems such that
  \begin{equation}
   \wM\left( \wn \right)  = \omega_k + \beta \left( \omega_{k+1} - \omega_k \right)
   \text{ with } 0 \leq \beta < 1
   \label{eq:chosenVariationOmega}
  \end{equation}
  where $\omega_k$ and $\omega_{k+1}$ are the excited grid lines closest to the frequency $\wM$ where the FRF has its peak amplitude and $\beta$ is the misalignment coefficient that is varied over the interval $[0,1]$.
  This means that $\omega_k \leq \wM \leq \omega_{k+1}$ and that $\beta$ replaces the $\gamma$ factor in \eqref{eq:theoreticalBestVariationOmega}.
  If we take a look at the special case when $\beta=0$ (or $\beta=1$) in this expression, we see that this situation occurs when the peak value of the FRF at $\wM$ coincides with the grid line $\omega_k$ or $\omega_{k+1}$ respectively.
  Basically, we study second order systems whose peak frequency $\wM$ is shifted between two neighboring excited frequency lines.
  From the previous section, we know that the exact frequency matters little as long as it remains within the bulk of the frequency grid.
  In this particular example $\wn$ was chosen at approximately $1 \unit{rad/s}$.

@@

  \TODO{simulations from Larsson2012}

### 2015-11-01 config/glossaries.inc.tex
Import SYSID2012 paper

%% SYMBOLS
\newsymbolglos{approx}{\approx}{Approximately equal}
\newsymbolglos{bydef}{\isdef}{Equal by definition}
\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{SetR}{\mathbb{R}}{Set of the real numbers}
\newsymbolglos{SetC}{\mathbb{C}}{Set of the complex numbers}
\newsymbolglos{SetN}{\mathbb{N}}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency or pulsation ($\omega = 2\pi f$) in $\unit{rad/s}$}
\newsymbolglos{f}{f}{Frequency in $\unit{Hz}$}

@@

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}

>>>>

%% SYMBOLS
\newsymbolglos{0-placeholder}{\placeholder}{Placeholder symbol}

\newsymbolglos{E-approx}{\approx}{Approximately equal}
\newsymbolglos{E-bydef}{\isdef}{Equal by definition}
\newsymbolglos{E-propto}{\propto}{Proportional to}

\newsymbolglos{norm}{\norm[p]{\placeholder}}{$p$-norm of a signal or system $\placeholder$}
\newsymbolglos{norm-hinf}{\norm[\infty]{\placeholder}}{\Hinf norm of the system $\placeholder$}
\newsymbolglos{norm-two}{\norm[2]{\placeholder}}{$\Hardy_{2}$ norm of the system $\placeholder$}

\newsymbolglos{imagunit}{j}{The imaginary unit, $j = \sqrt{-1}$}
\newsymbolglos{lcm}{\lcm}{Least common multiple}
\newsymbolglos{cardinality}{\numberOf \placeholder}{Number of elements (cardinality) in the set \placeholder}
\newsymbolglos{SetR}{\RealNumbers}{Set of the real numbers}
\newsymbolglos{SetZ}{\IntegerNumbers}{Set of integer numbers}
\newsymbolglos{SetC}{\ComplexNumbers}{Set of the complex numbers}
\newsymbolglos{SetN}{\NaturalNumbers}{Set of the natural numbers}
\newsymbolglos{w}{\omega}{Angular frequency (pulsation)}

\newsymbolglos{sys-resonance}{\wn}{Natural (resonance) frequency of a system}
\newsymbolglos{sys-damping}{\damping}{Relative damping of a system}
\newsymbolglos{sys-timeconst}{\tau}{Time constant of a system}

\newsymbolglos{count-mc}{n_{\mathrm{MC}}}{Number of Monte Carlo runs}
\newsymbolglos{count-theta}{n_{\theta}}{Number of parameters}

\newsymbolglos{operator-exp}{\expval{\placeholder}}{Expected value of \placeholder}
\newsymbolglos{operator-pinv}{\pinv{\placeholder}}{Moore-Penrose pseudo-inverse of the matrix \placeholder}
\newsymbolglos{operator-tran}{\placeholder^{\TT}}{Transpose of the matrix \placeholder}
\newsymbolglos{operator-ht}{\placeholder^{\HT}}{Hermitian transpose of the matrix \placeholder}

@@

\newacronym{LPM}{LPM}{Local Polynomial Method}
\newacronym{LRM}{LRM}{Local Rational Method}
\newacronym{LRIC}{LRIC}{Local Rational method with Iterative Cost function}
\newacronym{TRIMM}{TRIMM}{Transient Impulse Modeling}

\newacronym{RFIR}{RFIR}{Regularized Finite Impulse Response}

### 2015-11-01 front-and-back-matter/frontmatter.tex
Import SYSID2012 paper

\printglossary[type=\acronymtype,style=long,toctitle={Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,toctitle={List of Symbols}]

>>>>

\printglossary[type=\acronymtype,style=long,toctitle={List of Acronyms}, title={List of Acronyms}] %TODO: change format, set order, change title to "List of Abbreviations"
\glsaddall[types=symbols]
\printglossary[type=symbols,style=altlong4col,title={List of Symbols},toctitle={List of Symbols}]
